Reasoning About a Machine with Local Capabilities

### 2018-05-11 toplas/paper.tex
Minor things (label and removed empty tikz picture)
Moved things around in Appendix and added definitions related to the awkward example.

\definecolor{OliveGreen}{RGB}{60,128,49}
\definecolor{Blue}{RGB}{92,26,143}
\newenvironment{toplas}
    {\color{OliveGreen}

    }{}
\newenvironment{toplassug}
    {\color{Blue}

    }{}

@@

    \path[every node/.style={font=\sffamily\small}]
    (1l) edge (2l);
  \end{tikzpicture}
  \begin{tikzpicture}[main node/.style={}]
  \end{tikzpicture}
  \caption{Permission and locality hierarchy.}
  \label{fig:perm-hier}
\end{wrapfigure}

@@

    % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbracebotred{(4.6,2)}{(4.6,12)}{sp}
      \end{scope}
      \begin{scope}
        \clip (5.6,6.6) rectangle (9,11.5);
        \capbrace{(5.6,6.5)}{(5.6,12)}{sp'}
      \end{scope}
    \end{tikzpicture}
  \caption{}
  \label{fig:illu-adv-called}
  \end{subfigure}
  \caption{Illustration of the situations related to stack clearing when invoking an adversary.
    The greyed out areas are parts of the stack that are not accessible at the time.
  }
  \label{fig:ret-adv}
\end{figure}

@@

>>>>

\definecolor{OliveGreen}{RGB}{60,128,49}
\definecolor{Blue}{RGB}{92,26,143}
\newenvironment{toplas}
    {\color{OliveGreen}}{}
\newenvironment{toplassug}
    {\color{Blue}}{}

@@

    \path[every node/.style={font=\sffamily\small}]
    (1l) edge (2l);
  \end{tikzpicture}
  \caption{Permission and locality hierarchy.}
  \label{fig:perm-hier}
\end{wrapfigure}

@@

    % Stack pointer
      \begin{scope}
        \clip (4.6,2) rectangle (7.6,11.5);
        \capbracebotred{(4.6,2)}{(4.6,12)}{sp}
      \end{scope}
      \begin{scope}
        \clip (5.6,6.6) rectangle (9,11.5);
        \capbrace{(5.6,6.5)}{(5.6,12)}{sp'}
      \end{scope}
    \end{tikzpicture}
  \caption{}
  \label{fig:illu-adv-called}
  \end{subfigure}
  \caption{Illustration of the situations related to stack clearing when invoking an adversary.
    The greyed out areas are parts of the stack that are not accessible at the time.
  }
  \label{fig:invoke-adv}
\end{figure}

@@

\subsection{Awkward example}
\textbf{The region for $x$} The region $\iota_x$, is the region omitted from the proof sketch for the awkward example.
\figurename~\ref{fig:x-reg} illustrates the transition system of $\iota_x$.
  \begin{figure}[tb]
    \centering
\begin{tikzpicture}[->,shorten >=1pt,auto,node distance=3cm,
  thick,main node/.style={circle,fill=white,draw,font=\sffamily\large},rect node/.style={rectangle,fill=blue!20,draw,font=\sffamily\large}]

  \node[main node] (n0) {\footnotesize $\texttt{x}=0$};
  \node (s) [left of=n0,xshift=1.75cm] {  };
  \node[main node] (n1) [right of=n0]  {\footnotesize $\texttt{x}=1$};
  \draw (s) edge[>=stealth] (n0);
  \draw (n0) edge[bend left,>=stealth] (n1);
  \draw (n1) edge[bend left,dashed,>=stealth] (n0);

\end{tikzpicture}
  \caption{Illustration of transition system in $\iota_x$. The dashed line is
    the private transition.}
  \label{fig:x-reg}
\end{figure}

\begin{definition}
  \label{def:iotax-region}
  \begin{align*}
    \iota_x   & = (\perm, 0, \phi_\pub, \phi, H_x) \\
    \phi_\pub & = \{(0,1)\}^* \\
    \phi      & = (1,0) \union \phi_\pub \\
    H_x \; s \; \hat{W} & = \{\npair{\ms} \mid \ms(x) = s \land n > 0 \} \union \{\npair[0]{\ms}\}
  \end{align*}
\end{definition}
\textbf{Static region} This static region only requires that the memory segment is the given one.
As it does not require safety, capabilities for this region cannot be gives to adversarial code.
\begin{align*}
  \iota^\sta (v,\ms) &= (v,1,=,=,H^\sta\;\ms)\\
  H^\sta \; \ms \; s \; \hat{W} = & \{\npair{\ms} \mid n > 0 \} \union \{\npair[0]{\ms'} \mid \ms' \in \Mems \}
\end{align*}
\textbf{Static safe region} Static region that also requires safety.
It is safe to give adversarial code read capabilities for this region.
\begin{align*}
  \iota^{\sta,u} (v,\ms) &= (v,1,=,=,H^{\sta,u}\;\ms)\\
  H^{\sta,u} \; \ms \; s \; \hat{W} = & \left\{\npair{\ms'} \middle|
    \begin{aligned}
      &\ms' = \ms \land\\
      &\forall \addr \in \dom(\ms) \ldotp\\
      & \quad \nonlocal{\ms(\addr)} \land\\
      & \quad \npair[n-1]{\ms(\addr)} \in \stdvr(\xi(\hat{W}))
    \end{aligned}
        \right\} \union \{\npair[0]{\ms'} \mid \ms' \in \Mems \}
\end{align*}
